Asteroid project summary

### 2021-11-12 summaries/hamiltonian/21-11.tex
resolve problem

To calculate the kinetic energy, we write the angular velocity in the body-fixed frame in terms of the Euler angles:
\begin{equation}
\bm \omega_{xyz} = \parens{\begin{matrix}
0 & -\sin \alpha & \sin \beta \cos \alpha \\
0 & \cos \alpha & \sin \beta \sin \alpha \\
1 & 0 & \cos \beta
\end{matrix}}
\parens{\begin{matrix}
\dot \alpha\\
\dot \beta \\
\dot \gamma
\end{matrix}}.
\label{eqn:ang-vel}
\end{equation}
The rotational kinetic energy is then
\begin{equation}
K = \frac{1}{2} \bm\omega^T I \bm \omega
\label{eqn:ke}
\end{equation}
where $\bm \omega$ and $I$ are both given in the body-fixed frame.

@@

For the initial conjugate momenta, we use equation \ref{eqn:momenta} and the fact that $\bm \omega_{xyz}=\omega \unit z$ at the initial position. Specifically:
\begin{equation}
\bm p_0 = \frac{2}{3}\mu_m a_m^2 (-2K_{20}+1) \omega \parens{\begin{matrix}1 \\0 \\ \cos \beta\end{matrix}}.
\end{equation}

>>>>

To calculate the kinetic energy, we write the angular velocity in the inertial frame in terms of the Euler angles:
\begin{equation}
\bm \omega_{XYZ} = \parens{\begin{matrix}
-\sin\beta \cos \gamma & \sin \gamma & 0\\
\sin \beta \sin \gamma & \cos \gamma & 0 \\
\cos \beta & 0 & 1
\end{matrix}}
\parens{\begin{matrix}
\dot \alpha\\
\dot \beta \\
\dot \gamma
\end{matrix}}.
\label{eqn:ang-vel}
\end{equation}
The rotational kinetic energy is then
\begin{equation}
K = \frac{1}{2} \bm\omega_{XYZ}^T M I M^T \bm \omega_{XYZ}
\label{eqn:ke}
\end{equation}
where $\bm \omega$ and $I$ are both given in the body-fixed frame.

\jtd{The below does not have the Ms here because I added them after realizing that it's invalid to write $K$ in the rotating frame. But it complicates the derivatives too much.}

@@

For the initial conjugate momenta, we use equation \ref{eqn:momenta} and the fact that $\bm \omega_{xyz}=\omega \unit z$ at the initial position. Specifically:
\begin{equation}
\bm p_0 = \frac{2}{3}\mu_m a_m^2 (-2K_{20}+1) \omega \parens{\begin{matrix}1 \\0 \\ \cos \beta\end{matrix}}.
\end{equation}
If in fact $\omega_{xyz} = \omega \unit z + \epsilon \omega \unit x$, we would have
